### 2017-06-05 article.tex
Initial import

\documentclass[a4paper,10pt,onecolumn]{article}

% Wider margins (compared to default)
\usepackage[margin=2.5cm]{geometry}

% English support (typography and hyphenation)
\usepackage[american]{babel}
\usepackage{csquotes}

% For math
\usepackage{amsmath}

% Unicode encoding
\usepackage[utf8]{inputenc}

% Better default font (Libertine and Inconsolata)
\usepackage[ttscale=.875]{libertine}
\usepackage[scaled=0.96]{zi4}

% Biber
\usepackage[backend=biber,
            style=apa,
            % backref=true,
            % backrefstyle=three,
            maxcitenames=3,
            maxbibnames=99,
            apamaxprtauth=99,
            natbib=true]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

% Figure & graphics
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{graphicx}

% Figure caption
\usepackage[labelsep=period]{caption}
\captionsetup[figure]{font=small,skip=0pt}
\renewcommand{\captionfont}{\small\sffamily}
\renewcommand{\captionlabelfont}{\small\sffamily\bfseries}

% Hyperref
\usepackage{xcolor}
\definecolor{blendedblue}{rgb}{0.2, 0.2, 0.6}
\definecolor{blendedred}{rgb}{0.8, 0.2, 0.2}
\usepackage[bookmarks=true,
            breaklinks=true,
            pdfborder={0 0 0},
            citecolor=blendedblue,
            colorlinks=true,
            linkcolor=blendedblue,
            urlcolor=blendedblue,
            citecolor=blendedblue,
            linktocpage=false,
            hyperindex=true,
            linkbordercolor=white]{hyperref}
\usepackage{hyperref}
\hypersetup{colorlinks=true}

% Bibliography file
\bibliography{article.bib}

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf \today}
\lhead{\footnotesize \sf NP Rougier \textbullet~Ten Simple Rules for Fraud \& Misconduct}
%% \rfoot{}
%% \cfoot{}
%% \lfoot{}

\makeatletter
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
  \textbf{\huge\@title\\}
  \vspace{5mm}
  \@author
\end{flushleft}\egroup
}
\makeatother

\title{Ten Simple Rules for Fraud \& Misconduct}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          33405 Talence, France
    $^{2}$Institut des Maladies Neurodégénératives,
          Université de Bordeaux, CNRS UMR 5293,
          33000, Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, 33405 Talence, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}
  \end{footnotesize}
}

\date{\today}

\begin{document}
\maketitle

\begin{tikzpicture}[remember picture, overlay]
    \node[xshift=-2.85cm,yshift=-2.85cm] at (current page.north east) {
        \includegraphics[width=3cm]{stample}
    };
\end{tikzpicture}

\begin{figure}[h]
  \begin{center}
    \noindent \includegraphics[width=\textwidth]{fraud-kit}
  \end{center}
  \caption{My First Fraud Kit. Copyright (c) 2012 Aurich Lawson. Ars Technica
    \citep{timmer:2012}.}
\end{figure}

\section*{Introduction}

So, here we are! You've decided to join the dark side of Science. That's great!
You'll soon discover a brand new world of shiny and surprising results,
non-replicable experiments, fabricated data, funny statistics, fame and shame,
joy and sadness, and... jail. But you've made your choice (for whatever
reasons) and you better have to be well prepared because Science is strong on
the other side. Only a few years from now, fraud and misconduct was a piece of
cake (\href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
\href{https://en.wikipedia.org/wiki/Charles_Redheffer}{Perpetual motion
  machine}, \href{https://en.wikipedia.org/wiki/Great_Moon_Hoax}{Life on Moon},
\href{https://en.wikipedia.org/wiki/Piltdown_Man}{Piltdown man},
\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). Problem is
that there are new players in town (\href{https://pubpeer.com}{PubPeer},
\href{http://retractionwatch.com}{RetractionWatch},
\href{https://forbetterscience.com}{For Better Science},
\href{http://blogs.discovermagazine.com/neuroskeptic/}{Neuroskeptic} to name
just a few) and they're pretty good at spotting and reporting fraudsters.
Furthermore, publishers have started to retaliate with pretty high-tech heavy
machinery such that to commit fraud or misconduct without getting caught in
2017 is kind of a challenge. But there will be always people that think they're
smarter than a whole community. And because we love to have things done in the
proper way, we're kind enough to give you some simple rules to follow in your
brand new career (see also \citep{timmer:2012} for a set of complementary
rules). However, results and consequences are not guaranteed.

\section*{Rule 1: Misrepresent, falsify or fabricate your data}

In order to start a plain and deceitful scientific fraudster life, the very
first thing you need to gain expertise on is to learn how to convincingly
misrepresent, falsify or fabricate your data. If you're still hesitating at
embracing the dark side of Science, you may start with a slight
mis-representation to strengthen your hypothesis. Some classical
techniques are illustrated in the seventh rule of the Ten Simple Rules for
Better Figures \citep{rougier:2014} article but there are actually
\href{https://en.wikipedia.org/wiki/Misleading_graph}{many more techniques} to
make a graph misleading \citep{wainer:1984,raschke:2008}. You can also directly
change your results in a post-production phase by using software such as
Photoshop or Gimp that makes it really easy to change pretty much anything in a
figure \citep{cromey:2012, hendricks:2011}. But be careful of not making too
obvious manipulations because an ever-growing number of journals are now
equipped with forensic software to spot image manipulation \citep{white:2007,
  rossner:2004,hsu:2015} (see also
\href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
  image manipulation recommendation}). You can even test your image online
using \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
by Jonas Wagner. This should dissuade you from manipulating your image by
yourself.\\
%
\begin{wrapfigure}{r}{0.4\textwidth}
%  \vspace{-8mm}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{datasaurus}
  \end{center}
  \caption{The Datasaurus set by \href{http://www.thefunctionalart.com/2016/08/download-datasaurus-never-trust-summary.html}{Alberto Cairo}. }
  \label{fig:datasaurus}
\end{wrapfigure}
%
Because none of the above techniques will change the statistics of your data,
it might be better indeed to falsify your data. Starting with real data, you
can change only a few points in order to change a non-significant results into
an astoundingly highly significant result as shown on the
\href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
\citep{schonbrodt:2015}. The advantage of falsifying real data is that changing
only a few points will still make your data looks good and not too much
suspicious. The disadvantage is that it requires some real data in the first
place and thus it requires to carry on some actual experiment (i.e. some
work). As a last resort, you can also fabricate the whole dataset using a
specific program. For example, starting from a given X mean/SD, Y mean/SD, and
a correlation coefficient, you can generate a dataset with these precise
statistics \citep{matejka:2017}. Just make sure to not pick the datasaurus set
because if you plot it (see Fig. \ref{fig:datasaurus}), it might look
suspicious for the alert reader. By the way, make sure to have a backup story
when people will start asking or investigating how/when/where/how did you do
perform the experiments or this study. A number of misconducts have been
detected after just a few questions \citep{vastag:2006}.

\section*{Rule 2: Hack your results}

\begin{wrapfigure}{l}{0.4\textwidth}
  \vspace{-5mm}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{xkcd}
  \end{center}
  \caption{P-Values by XKCD (\url{https://xkcd.com/1478/}). This work is
    licensed under a CC-BY-NC 2.5 License.}
  \label{fig:xkcd}
\end{wrapfigure}
If you are reluctant at manipulating your data, you still have the option of
simply hacking your results in order to reach the significance level
(a.k.a. p-hacking). But before committing any scientific misconduct, are you
sure you need to do so? What is the p value of your NHST (Null Hypothesis
Significance Test)? Did you consider using one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} to report your results? Can't you use expression such as {\em nearly
acceptable level of significance (p=0.06)}, {\em very closely brushed the limit of
statistical significance (p=0.051)} or {\em weakly statistically significant
(p=0.0557)}?\\

However, if you're suffering from a bi-polar p-value disorder (term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the mythical 0.05 threshold whatever the
actual data and consequences. It might actually be much easier than you think
because the correct usage of the infamous p-value is hardly understood by a
number of students, teachers or researchers
\citep{haller:2002,lecoutre:2003}. The current situation is actually so bad
that the American Statistical Association had to release a statement to explain
the correct usage \citep{wasserstein:2016,} last year and Nature has issued as
well some warning on the usage of the p-value \citep{baker:2016}. Consequently,
before hacking your results, it might be wise to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014} if you want to take full advantage of the misuse of p-value.\\

Last, but not least, if you're in psychology, you have to take extra-precaution
because this domain has recently raised concerns, especially when it comes to
the unusual distribution of p-values smaller than 0.05
\citep{hartgerink:2016,bakker:2012}. If you add the statcheck variable into the
equation \citep{nuijten:2015,epskamp:2016}, it might be difficult to achieve a
proper p-hacking of your results and maybe it is time to reconsider your
commitment to the dark side of Science.

\section*{Rule 3: Copy/paste work from others}

You have your (fake) results but you still need to publish them to gain fame
(and tenure and professorship). Writing is a tedious task and might represent a
fair amount of work. Writing the state of the art in your domain requires to
actually read (what?) what your colleagues have been doing over the past few
years. It is a very time consuming task. But if one of these colleagues wrote a
nice introduction to the domain or a wonderful state of the art, why bother
writing a new one? Why not copy/paste what he/she has written instead?
Plagiarism is the nuts and bolts of scientific misconduct
\citep{neuroskeptic:2017}, be it literal copying, substantial copying or
paraphrasing (see
\href{https://www.elsevier.com/editors/perk/plagiarism-complaints}{definitions
  from Elsevier} and the committee on publication ethics (COPE) procedure to
handle plagiarism in a
\href{https://www.elsevier.com/__data/assets/pdf_file/0005/72815/plagiarism-A.pdf}{submitted}
or
\href{https://www.elsevier.com/__data/assets/pdf_file/0020/72830/plagiarism-B_0.pdf}{published}
article). Of course, you cannot literally copy paste an excerpt of text from an
article to insert it in yours. Just imagine a situation where the reviewer
would also be the author of the text being reviewed. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
detection by dedicated software (Plagiarism detection). These software are used
by universities and journals for tracking people just like you. And since their
database is really huge, plagiarism is harder and harder. Can you imagine than
self-plagiarism is not even allowed for a vast majority of journals? In the
end, you really have to improve or innovate in your techniques and to work very
hard \citep{long:2009}. But faced with such an adversarial nature of the
situation, to write your very own text might be an easier option.

\section*{Rule 4: Write your own peer-review}

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-5mm}
  \begin{center}
    \includegraphics[width=0.5\textwidth]{phd-comics}
  \end{center}
  \caption{Addressing reviewers comments. PhD Comics
    (\url{http://phdcomics.com}). Copyright (c) 2005 Jorge Cham.}
\end{wrapfigure}

Results and papers are ready and it is now time to submit. Depending on the
journal you target, you may still encounter some problem with the review
process. If reviewers are a bit too picky, they may ask you annoying questions,
be a bit suspicious, request more information, ask for a major revision and or
even reject your submission (can you imagine?). After all your hard work at
fabricating the data and plagiarized the article, that would be really
unfair. Fortunately, there is a simple solution. You can actually write your
own review! How is that possible you may ask? It is incredibly easy. At the
time of submission, you will be asked to give name of possible reviewers, just
give phony names with corresponding email addresses that will be redirected to
your mailbox. You will soon receive an invitation to review and you're then
free to write your own review and state how brilliant is your own work. Of
course, you'll have to write a review that looks like an actual review. If
you're Machiavellian, you will have introduced some factual errors in your
manuscript such that you can report them later in your review. Make sure also
to not send you review before the editor deadline because as
\href{https://arstechnica.com/science/2017/04/107-cancer-papers-retracted-due-to-peer-review-fraud/}{reported
  by Elizabeth Wager} \citep{stigbrand:2017}, one of the reasons the editors
spotted them was that the reviewers responded on time. However, editors and
publishers are now well aware of the scam \citep{ferguson:2014} and they have
taken counter-measure \citep{haug:2015}. For example, some of them do not offer
anymore the option to recommend unknown reviewer or if they do, the
recommendation is restricted to a list of certified reviewers. If you insist on
writing your own peer-review, you'll have to be creative and find new ways to
game the system.

\section*{Rule 5: Take advantage of predatory publishers}

If most journals will most likely reject your submission because you've applied
some of the rules above and get caught red-handed, you still have opportunities
to publish your results in one of the many predatory publishers available on
the internet and the internet only \citep{shen:2015}. Such predators will
publish just anything
(\href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
  Me Off Your Fucking Mailing List''} in the International Journal of Advanced
Computer Technology (2005, 2014)) and you have a 100\% chance to have your
article published with a lighting fast review (less than 24h for some
"journals"). Finding a predatory publisher used to be easy thanks to the list
created and maintained by Jeffrey Beal. Even if some people (and publishers)
have judged this list to be controversial, it was incredibly useful for a lot
of people. Unfortunately, this list has closed just a few months ago. But you
can now take advantage of the
\href{http://thinkchecksubmit.org}{Think/Check/Submit} website that provides a
easy-to-use checklist that researchers can refer to when they are investigating
whether a journal can be trusted. Just take the opposite of their wise
recommendations and make sure to \textbf{not} pick a journal from the list
\href{https://oaspa.org}{Open Access Scholarly Publishers Association} since
these journals have been thoroughly reviewed and can be trusted. For example,
if none of your colleagues know the journal, if the editorial board is made of
unknown or non-existent people \citep{sorokowski:2017} or even dogs in some
cases \citep{kennedy:2017} and no address / email / telephone is provided to
contact the publisher, you may have knocked at the right door. Of course, you
will have to pay exorbitant fees to have your work published, but this is the
price to pay to have an expedited and complaisant review (if any review at
all). Before making you decision where to publish, make sure to check as well
for the retraction fees that may be much higher than the initial publishing
fees in some cases. But who wants to retract anyway?

\section*{Rule 6: Don't give access to your code and data}

\begin{wrapfigure}{l}{0.4\textwidth}
  \vspace{-6mm}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{data-share}
  \end{center}
  \caption{Image by Ainsley Seago.}
  \label{fig:datasaurus}
\end{wrapfigure}

You managed to have your article published, congratulations! You'll probably
get a lot of buzz and mabye your amazing conclusion will make it to the
newspaper headline if your research is sexy enough. Because of the buzz,
chances are increased that people will start askink you to access your
material, if the publisher has not already requested it prior to
publication. Of course, that's quite a bad news for you because if your data
has been fabricated or if your statistical analysis is not really acamedic,
your colleagues might discover your misconduct. Consequently, you definitely
cannot give access to your raw material. For this, you can use the same old
reasons that have prevented data sharing for a very long time
\citep{roche:2014}: ``Oh you know, my data cannot be anonymized'', ``No, you
would not understand the structure of my data'', ``A lot of money has been
invested, I cannot give it for free'', etc. You can also tell people asking for
your data they are {\em research parasites} \citep{longo:2016} even though the
techniques seems to have backfired since then
(\url{http://researchparasite.com}).  Technological excuses might also be worth
a try. When \citep{collberg:2014,collberg:2015} tried to access the code of
several publications, they get some really great answers ``Too busy to help'',
``Code will be available soon'', ``Bad backup practice'', etc. Just pick one
you like. Finally, with the increasing pressure by institutions (NIH, NSF,
Europe, etc) to share data, you can pretend (and only pretend) to be a
supporter of Open Data by inserting a simple ``data available upon request'' or
``data is available from my website''. This does not correspond at all to the
FAIR principles (findable, accessible, interoperable, re-usable)
\citep{wilkinson:2016}, but who cares if you can give the illusion to not be
afraid of sharing your data? But don't get me wrong, you will never answer a
request, and the data will never appear on your website.

\section*{Rule 7: Do not allow for replication outside your lab}

Here comes the tricky part: replications. Can you imagine that some researchers
are willing to replicate your results based on what you've explained in your
article? \citep{nosek:2015} replicated 100 experiments reported in papers
published in three high-ranking psychology journal. Even worse, there is now a
dedicated scientific journals dedicated to replications
(e.g. \url{http://rescience.github.io}). If people start to replicate your work
and do not get the same results, you have a problem. You might be suspected of
fraud or misconduct and people will really insist on seeing you actual
data. You can try rule 6, but after several faild replication, it will be much
harder to deny access to your data. One easy way to avoid imminent disaster is
to claim beforehand in your article that the experiment/study has been already
replicated in your lab. The subliminal message to the reader is ``Don't bother
to replicate, we've already taken care of that and it works, believe us. Don't
lose your time, you will thank me later''. If this doesn't work, you can also
try a {\em Do Not Replicate order} as proposed by
\href{https://mchankins.wordpress.com/2014/07/12/do-not-replicate/}{Matthew
  Hankins} (who is kind enough as to provide a template). It is not yet widely
used, but we're confident editors will enforce the order.

\section*{Rule 8: Never, ever, retract your results}

If you've made a genuine (and big) mistake in your work, there is no problem in
asking for the retraction of your paper \citep{miller:2006}. This is actually
a behavior that is rewarded according to \citep{lu:2013}, even though in some
cases, it can take several years \citep{trivers:2009}. However, if you've been
frauding, having your paper retracted is like an admission of fraud and you
want to avoid that. Such retractation may start with a simple comment to the
editor saying there may be some problem with you paper. If you're lucky, such
comment, even if sound, will never make it into the journal
\citep{trebino:2009}, else, you'll have to give a convincing answer. Depending
how you adressed the comment, the editor can decide to retract your paper even
without your consent.  At this point of failure, you better start with a simple
corrigendum pretexting a bad preparation of the material for the publication.

\section*{Rule 9: Don't get caught. Deny if caught.}

If you intend to persist in your rogue scientific career, you have to know that
most likely, you'll get caught. The sooner or the later, but it will happen
eventually. The number of researcher to have never been caught is extremely low
and only the best can hope to be caught only after their death
\citep{degroote:2016,}. But being caught does not mean you career will come to
an end. There are actually a set of simple rules to deny having committed any
scientific misconduct:
\begin{itemize}
  \item If you're first author, explain you were supervised by last author and
    had no choice.
  \item If you're last author, explain you were not aware of the misconduct of
    the first author.
  \item If your name is not first nor last, explain you did not even know your
    name appeared in the publication.
  \item If your name appears because of {\em gift auhtorship}, just say it.
    It might be considered misconduct, but fraud is much worse.
  \item The intern, that cannot be contacted because he/she left academia is
    responsible for everything
  \item Send threat letter to those who have spotted your misconduct
  \item Sue'em all
\end{itemize}
If you're lucky enough, any of the above will do and things should be back to
normal, especially if you're supported by you employer because you're a rising
star.

\section*{Rule 10: }

\section*{Conclusion}

By following the simple rules above, you should get an instantaneous (but
brief) scientific glory, possibly followed by a jail sentence. Nothing comes
for free. Since 2015, scientific misconduct can officialy lead you to jail
\citep{grant:2015}. More precisely, a former researcher has been sentenced to
57 months jail and to pay-back 7.2 millions dollars. Science has been and is
still poisoned by fraud and misconduct, but it is now fighting back and the
high-tech war has begun \citep{buranyi:2017}. Today, the risks associated with
fraud and misconduct are really high as well as the chances of being
caught. Consequently, you'd better think twice before committing misconduct or
your name will soon appear in the
\href{https://en.wikipedia.org/wiki/Scientific_misconduct#Notable_individual_cases}{hall
  of shame}.

% -------------------------------------------------------------- References ---
\renewcommand*{\bibfont}{\small}
\printbibliography[title=References]
\end{document}

### 2017-06-16 article.tex
First complete draft

@@
 % Wider margins (compared to default)
-\usepackage[margin=2.5cm]{geometry}
+%\usepackage[margin=2.5cm]{geometry}
+\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
 
@@
 \usepackage[utf8]{inputenc}
+
+% Color box
+\usepackage{tikz}
+\usepackage[most]{tcolorbox}
 
@@
 \lhead{\footnotesize \sf NP Rougier \textbullet~Ten Simple Rules for Fraud \& Misconduct}
-%% \rfoot{}
-%% \cfoot{}
-%% \lfoot{}
+\rfoot{\footnotesize \sf \thepage}
+\cfoot{}
+\lfoot{}
 
@@
     $^{1}$INRIA Bordeaux Sud-Ouest
-          33405 Talence, France
+          Talence, France
     $^{2}$Institut des Maladies Neurodégénératives,
           Université de Bordeaux, CNRS UMR 5293,
-          33000, Bordeaux, France
+          Bordeaux, France
     $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-          CNRS, UMR 5800, 33405 Talence, France\\
+          CNRS, UMR 5800, Talence, France\\
     $^{*}$Corresponding author:
@@
 
-\begin{figure}[h]
-  \begin{center}
-    \noindent \includegraphics[width=\textwidth]{fraud-kit}
-  \end{center}
-  \caption{My First Fraud Kit. Copyright (c) 2012 Aurich Lawson. Ars Technica
-    \citep{timmer:2012}.}
-\end{figure}
+%% \begin{figure}[h]
+%%   \begin{center}
+%%     \noindent \includegraphics[width=\textwidth]{fraud-kit}
+%%   \end{center}
+%%   \caption{My First Fraud Kit. Copyright (c) 2012 Aurich Lawson. Ars Technica
+%%     \citep{timmer:2012}.}
+%% \end{figure}
+
+\begin{tcolorbox}[breakable, pad at break*=1mm,
+    colback=yellow!5, arc=0pt, outer arc=0pt, boxrule=0pt, frame hidden]
+\begin{small}
+\noindent {\sf \textbf{Disclaimer.} We do not encourage scientific fraud nor
+  misconduct. The goal of this provocative article is to alert the reader on a
+  preoccupying situation in Science. Facing the Publish or Perish alternative,
+  a number of researchers have decided to cross the Rubicon without the full
+  knowledge of the dramatic consequences that may hurt Science and impact not
+  only their scientific life but their actual life as well. If you're tempted
+  to (even so slightly) beautify your results, keep in mind that the game is
+  probably not worth the risks.}\par
+\end{small}
+\end{tcolorbox}
 
@@
 just a few) and they're pretty good at spotting and reporting fraudsters.
-Furthermore, publishers have started to retaliate with pretty high-tech heavy
-machinery such that to commit fraud or misconduct without getting caught in
-2017 is kind of a challenge. But there will be always people that think they're
-smarter than a whole community. And because we love to have things done in the
-proper way, we're kind enough to give you some simple rules to follow in your
-brand new career (see also \citep{timmer:2012} for a set of complementary
-rules). However, results and consequences are not guaranteed.
+Furthermore, publishers have started to retaliate with high-tech tools. To
+commit fraud or misconduct without getting caught in 2017 is kind of a
+challenge and requires a real dedication to your task. But there will be always
+people that think they're smarter than a whole community. And because we love
+to have things done in the proper way, we're kind enough to give you some
+simple rules to follow in your brand new career (see also \citep{timmer:2012}
+for a set of complementary rules). However, results and consequences are not
+guaranteed.
 
@@
 embracing the dark side of Science, you may start with a slight
-mis-representation to strengthen your hypothesis. Some classical
-techniques are illustrated in the seventh rule of the Ten Simple Rules for
-Better Figures \citep{rougier:2014} article but there are actually
-\href{https://en.wikipedia.org/wiki/Misleading_graph}{many more techniques} to
-make a graph misleading \citep{wainer:1984,raschke:2008}. You can also directly
-change your results in a post-production phase by using software such as
-Photoshop or Gimp that makes it really easy to change pretty much anything in a
-figure \citep{cromey:2012, hendricks:2011}. But be careful of not making too
-obvious manipulations because an ever-growing number of journals are now
-equipped with forensic software to spot image manipulation \citep{white:2007,
-  rossner:2004,hsu:2015} (see also
+mis-representation to strengthen your hypothesis. Some classical techniques are
+illustrated in the seventh rule of \citep{rougier:2014} but there are
+actually \href{https://en.wikipedia.org/wiki/Misleading_graph}{many more
+  techniques} to make a graph misleading \citep{wainer:1984,raschke:2008}. You
+can also directly change your results in a post-production phase by using
+software such as Photoshop or Gimp that makes it really easy to change pretty
+much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful
+of not making too obvious manipulations because an ever-growing number of
+journals are now equipped with forensic software to spot image manipulation
+\citep{white:2007, rossner:2004,hsu:2015} (see also
 \href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
@@
 by Jonas Wagner. This should dissuade you from manipulating your image by
-yourself.\\
+yourself.
 %
-\begin{wrapfigure}{r}{0.4\textwidth}
-%  \vspace{-8mm}
-  \begin{center}
-    \includegraphics[width=0.4\textwidth]{datasaurus}
-  \end{center}
-  \caption{The Datasaurus set by \href{http://www.thefunctionalart.com/2016/08/download-datasaurus-never-trust-summary.html}{Alberto Cairo}. }
-  \label{fig:datasaurus}
-\end{wrapfigure}
+%% \begin{wrapfigure}{r}{0.4\textwidth}
+%% %  \vspace{-8mm}
+%%   \begin{center}
+%%     \includegraphics[width=0.4\textwidth]{datasaurus}
+%%   \end{center}
+%%   \caption{The Datasaurus set by \href{http://www.thefunctionalart.com/2016/08/download-datasaurus-never-trust-summary.html}{Alberto Cairo}. }
+%%   \label{fig:datasaurus}
+%% \end{wrapfigure}
 %
-Because none of the above techniques will change the statistics of your data,
-it might be better indeed to falsify your data. Starting with real data, you
-can change only a few points in order to change a non-significant results into
-an astoundingly highly significant result as shown on the
+Furthermore, none of the previous techniques will change the statistics of your
+data and it might a better choice to falsify your data. Starting with real
+data, you can change only a few points in order to change a non-significant
+results into an astoundingly highly significant result as shown on the
 \href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
-\citep{schonbrodt:2015}. The advantage of falsifying real data is that changing
+\citep{schonbrodt:2015} or the interactive applet from
+\citep{aschwanden:2015}. The advantage of falsifying real data is that changing
 only a few points will still make your data looks good and not too much
@@
 place and thus it requires to carry on some actual experiment (i.e. some
-work). As a last resort, you can also fabricate the whole dataset using a
+work). As a last resort, you can also fabricate the whole data set using a
 specific program. For example, starting from a given X mean/SD, Y mean/SD, and
-a correlation coefficient, you can generate a dataset with these precise
-statistics \citep{matejka:2017}. Just make sure to not pick the datasaurus set
-because if you plot it (see Fig. \ref{fig:datasaurus}), it might look
-suspicious for the alert reader. By the way, make sure to have a backup story
-when people will start asking or investigating how/when/where/how did you do
-perform the experiments or this study. A number of misconducts have been
-detected after just a few questions \citep{vastag:2006}.
+a correlation coefficient, you can generate a data set with these precise
+statistics \citep{matejka:2017}. Do not pick the datasaurus set because if you
+plot it, it might look suspicious for the alert reader. Finally, make sure to
+have a backup story when people will start asking or investigating
+how/when/where/how did you do perform the experiments to get these data. A
+number of misconducts have been detected after just a few questions
+\citep{vastag:2006}.
 
@@
 
-\begin{wrapfigure}{l}{0.4\textwidth}
-  \vspace{-5mm}
-  \begin{center}
-    \includegraphics[width=0.4\textwidth]{xkcd}
-  \end{center}
-  \caption{P-Values by XKCD (\url{https://xkcd.com/1478/}). This work is
-    licensed under a CC-BY-NC 2.5 License.}
-  \label{fig:xkcd}
-\end{wrapfigure}
+%% \begin{wrapfigure}{l}{0.4\textwidth}
+%%   \vspace{-5mm}
+%%   \begin{center}
+%%     \includegraphics[width=0.4\textwidth]{xkcd}
+%%   \end{center}
+%%   \caption{P-Values by XKCD (\url{https://xkcd.com/1478/}). This work is
+%%     licensed under a CC-BY-NC 2.5 License.}
+%%   \label{fig:xkcd}
+%% \end{wrapfigure}
 If you are reluctant at manipulating your data, you still have the option of
@@
   Hankins} to report your results? Can't you use expression such as {\em nearly
-acceptable level of significance (p=0.06)}, {\em very closely brushed the limit of
-statistical significance (p=0.051)} or {\em weakly statistically significant
-(p=0.0557)}?\\
+  acceptable level of significance (p=0.06)}, {\em very closely brushed the
+  limit of statistical significance (p=0.051)} or {\em weakly statistically
+  significant (p=0.0557)}? It does not make sense, but in some cases, it might
+be sufficient to convince a naive reviewer or reader. However, if you're
+suffering from a bi-polar p-value disorder (term coined by
+\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
+  Lakens}), you'll want to reach the magical 0.05 threshold and it might
+actually be much easier than you think because the correct usage of the
+infamous p-value is hardly understood by a number of students, teachers or
+researchers \citep{haller:2002,lecoutre:2003}. The current situation is
+actually so bad that the American Statistical Association had to release a
+statement to explain the correct usage \citep{wasserstein:2016,} last year and
+Nature has issued as well some warning on the usage of the p-value
+\citep{baker:2016}. Consequently, before hacking your results, it might be wise
+to re-read your classics
+\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014} if you want to
+take full advantage of the misuse of p-value. Last, but not least, if you're in
+psychology, you have to take extra-precaution because this domain has recently
+raised concerns, especially when it comes to the unusual distribution of
+p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. If you add the
+statcheck variable into the equation \citep{nuijten:2015,epskamp:2016}, it
+might be difficult to achieve a proper p-hacking of your results without being
+noticed. Even though some people would call such results checking {\em
+  methodological terrorism} \citep{finske:2016}, it might be time to reconsider
+your commitment to the dark side of Science.
 
-However, if you're suffering from a bi-polar p-value disorder (term coined by
-\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
-  Lakens}), you'll want to reach the mythical 0.05 threshold whatever the
-actual data and consequences. It might actually be much easier than you think
-because the correct usage of the infamous p-value is hardly understood by a
-number of students, teachers or researchers
-\citep{haller:2002,lecoutre:2003}. The current situation is actually so bad
-that the American Statistical Association had to release a statement to explain
-the correct usage \citep{wasserstein:2016,} last year and Nature has issued as
-well some warning on the usage of the p-value \citep{baker:2016}. Consequently,
-before hacking your results, it might be wise to re-read your classics
-\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014} if you want to take full advantage of the misuse of p-value.\\
+\section*{Rule 3: Copy/paste from others}
 
-Last, but not least, if you're in psychology, you have to take extra-precaution
-because this domain has recently raised concerns, especially when it comes to
-the unusual distribution of p-values smaller than 0.05
-\citep{hartgerink:2016,bakker:2012}. If you add the statcheck variable into the
-equation \citep{nuijten:2015,epskamp:2016}, it might be difficult to achieve a
-proper p-hacking of your results and maybe it is time to reconsider your
-commitment to the dark side of Science.
-
-\section*{Rule 3: Copy/paste work from others}
-
-You have your (fake) results but you still need to publish them to gain fame
-(and tenure and professorship). Writing is a tedious task and might represent a
-fair amount of work. Writing the state of the art in your domain requires to
-actually read (what?) what your colleagues have been doing over the past few
-years. It is a very time consuming task. But if one of these colleagues wrote a
-nice introduction to the domain or a wonderful state of the art, why bother
-writing a new one? Why not copy/paste what he/she has written instead?
-Plagiarism is the nuts and bolts of scientific misconduct
+You have your (fake) results but you still need to publish your clickbait
+article to gain fame (and tenure and professorship). Writing is a tedious task
+and might represent a fair amount of work. Writing the state of the art in your
+domain requires to actually read (what?) what your colleagues have been doing
+over the past few years. It is a very time consuming task. But if one of these
+colleagues wrote a nice introduction to the domain or a wonderful state of the
+art, why bother writing a new one? Why not copy/paste what he/she has written
+instead?  Plagiarism is the nuts and bolts of scientific misconduct
 \citep{neuroskeptic:2017}, be it literal copying, substantial copying or
@@
 avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
-detection by dedicated software (Plagiarism detection). These software are used
-by universities and journals for tracking people just like you. And since their
+detection by dedicated software (e.g. iThenticate). These software are used by
+universities and journals for tracking people just like you. And since their
 database is really huge, plagiarism is harder and harder. Can you imagine than
@@
 
-\begin{wrapfigure}{r}{0.5\textwidth}
-  \vspace{-5mm}
-  \begin{center}
-    \includegraphics[width=0.5\textwidth]{phd-comics}
-  \end{center}
-  \caption{Addressing reviewers comments. PhD Comics
-    (\url{http://phdcomics.com}). Copyright (c) 2005 Jorge Cham.}
-\end{wrapfigure}
+%% \begin{wrapfigure}{r}{0.5\textwidth}
+%%   \vspace{-5mm}
+%%   \begin{center}
+%%     \includegraphics[width=0.5\textwidth]{phd-comics}
+%%   \end{center}
+%%   \caption{Addressing reviewers comments. PhD Comics
+%%     (\url{http://phdcomics.com}). Copyright (c) 2005 Jorge Cham.}
+%% \end{wrapfigure}
 
@@
   by Elizabeth Wager} \citep{stigbrand:2017}, one of the reasons the editors
-spotted them was that the reviewers responded on time. However, editors and
+spotted fake reviews was that reviewers responded just in time. However, editors and
 publishers are now well aware of the scam \citep{ferguson:2014} and they have
-taken counter-measure \citep{haug:2015}. For example, some of them do not offer
+taken counter-measures \citep{haug:2015}. For example, some of them do not offer
 anymore the option to recommend unknown reviewer or if they do, the
@@
 Computer Technology (2005, 2014)) and you have a 100\% chance to have your
-article published with a lighting fast review (less than 24h for some
-"journals"). Finding a predatory publisher used to be easy thanks to the list
+article published with a lighting fast review, less than 24h for some
+journals. Finding a predatory publisher used to be easy thanks to the list
 created and maintained by Jeffrey Beal. Even if some people (and publishers)
 have judged this list to be controversial, it was incredibly useful for a lot
-of people. Unfortunately, this list has closed just a few months ago. But you
-can now take advantage of the
+of people. Unfortunately, this list has closed just a few months ago
+\citep{straumsheim:2017} and the
+soon-to-be released replacement one will not be free \citep{silver:2017}. But
+you can now take advantage of the
 \href{http://thinkchecksubmit.org}{Think/Check/Submit} website that provides a
@@
 will have to pay exorbitant fees to have your work published, but this is the
-price to pay to have an expedited and complaisant review (if any review at
-all). Before making you decision where to publish, make sure to check as well
+price to pay to have an expedited and complaisant review, if any review at
+all. Before making you decision where to publish, make sure to check as well
 for the retraction fees that may be much higher than the initial publishing
@@
 
-\begin{wrapfigure}{l}{0.4\textwidth}
-  \vspace{-6mm}
-  \begin{center}
-    \includegraphics[width=0.4\textwidth]{data-share}
-  \end{center}
-  \caption{Image by Ainsley Seago.}
-  \label{fig:datasaurus}
-\end{wrapfigure}
+%% \begin{wrapfigure}{l}{0.4\textwidth}
+%%   \vspace{-6mm}
+%%   \begin{center}
+%%     \includegraphics[width=0.4\textwidth]{data-share}
+%%   \end{center}
+%%   \caption{Image by Ainsley Seago.}
+%%   \label{fig:datasaurus}
+%% \end{wrapfigure}
 
 You managed to have your article published, congratulations! You'll probably
-get a lot of buzz and mabye your amazing conclusion will make it to the
-newspaper headline if your research is sexy enough. Because of the buzz,
-chances are increased that people will start askink you to access your
+get a lot of buzz and maybe your amazing conclusion will make it to the
+newspaper headlines if your research is sexy enough. Because of the buzz,
+chances are increased that people will start asking you to access your
 material, if the publisher has not already requested it prior to
 publication. Of course, that's quite a bad news for you because if your data
-has been fabricated or if your statistical analysis is not really acamedic,
+has been fabricated or if your statistical analysis is not really academic,
 your colleagues might discover your misconduct. Consequently, you definitely
@@
 would not understand the structure of my data'', ``A lot of money has been
-invested, I cannot give it for free'', etc. You can also tell people asking for
-your data they are {\em research parasites} \citep{longo:2016} even though the
-techniques seems to have backfired since then
+invested, I cannot give it for free'', etc. You can also tell these people
+asking for your data that they are {\em research parasites} \citep{longo:2016}
+even though the techniques seems to have backfired since then
 (\url{http://researchparasite.com}).  Technological excuses might also be worth
@@
 ``data is available from my website''. This does not correspond at all to the
-FAIR principles (findable, accessible, interoperable, re-usable)
-\citep{wilkinson:2016}, but who cares if you can give the illusion to not be
+FAIR principles (findable, accessible, inter-operable, re-usable,
+\cite{wilkinson:2016}), but who cares if you can give the illusion to not be
 afraid of sharing your data? But don't get me wrong, you will never answer a
@@
 article? \citep{nosek:2015} replicated 100 experiments reported in papers
-published in three high-ranking psychology journal. Even worse, there is now a
-dedicated scientific journals dedicated to replications
+published in three high-ranking psychology journal. And of course, they
+concluded that some experiments were not replicable at all. How surprising!
+Even worse, there is now scientific journals dedicated to replications
 (e.g. \url{http://rescience.github.io}). If people start to replicate your work
@@
 fraud or misconduct and people will really insist on seeing you actual
-data. You can try rule 6, but after several faild replication, it will be much
+data. You can try rule 6, but after several failed replication, it will be much
 harder to deny access to your data. One easy way to avoid imminent disaster is
@@
 to replicate, we've already taken care of that and it works, believe us. Don't
-lose your time, you will thank me later''. If this doesn't work, you can also
+lose your time, you will thank us later''. If this doesn't work, you can also
 try a {\em Do Not Replicate order} as proposed by
@@
   Hankins} (who is kind enough as to provide a template). It is not yet widely
-used, but we're confident editors will enforce the order.
+used yet, but with the replication crisis we're facing in several scientific
+domain, we're confident it will soon become popular.
 
@@
 If you've made a genuine (and big) mistake in your work, there is no problem in
-asking for the retraction of your paper \citep{miller:2006}. This is actually
-a behavior that is rewarded according to \citep{lu:2013}, even though in some
+asking for the retraction of your paper \citep{miller:2006}. This is actually a
+behavior that is rewarded according to \citep{lu:2013}, even though in some
 cases, it can take several years \citep{trivers:2009}. However, if you've been
 frauding, having your paper retracted is like an admission of fraud and you
-want to avoid that. Such retractation may start with a simple comment to the
+want to avoid that. Such retraction may start with a simple comment to the
 editor saying there may be some problem with you paper. If you're lucky, such
@@
 \citep{trebino:2009}, else, you'll have to give a convincing answer. Depending
-how you adressed the comment, the editor can decide to retract your paper even
-without your consent.  At this point of failure, you better start with a simple
-corrigendum pretexting a bad preparation of the material for the publication.
+how you addressed the comment, the editor can decide to retract your paper even
+without your consent. Before reaching this failure climax, you better have to
+start with a simple corrigendum pretexting a bad preparation of the material
+for the publication.  Don't hesitate to publish as many corrigendum as
+necessary to make critics happy. This can last for several years, the time
+needed for people to forget about your fraud or misconduct.
 
@@
 \citep{degroote:2016,}. But being caught does not mean you career will come to
-an end. There are actually a set of simple rules to deny having committed any
+an end. There is actually a set of simple rules to deny having committed any
 scientific misconduct:
@@
     name appeared in the publication.
-  \item If your name appears because of {\em gift auhtorship}, just say it.
+  \item If your name appears because of {\em gift authorship}, just say it.
     It might be considered misconduct, but fraud is much worse.
@@
 If you're lucky enough, any of the above will do and things should be back to
-normal, especially if you're supported by you employer because you're a rising
-star.
+normal, especially if you're supported by you employer because you've been
+labeled as a rising star.
 
-\section*{Rule 10: }
+\section*{Rule 10: Be creative (for once)}
+
+If you look at the yearly list of
+\href{http://www.the-scientist.com/?articles.view/articleNo/47813/title/Top-10-Retractions-of-2016/}{top
+  ten retractions} compiled by Adam Marcus and Ivan Oransky (co-founders of the
+RetractionWatch) since 2012, you'll realize that all the above rules are
+already quite well known in the community. If you want to stay off the radar
+while committing fraud and misconduct, you'll have to be creative and invent
+new rules.
 
@@
 By following the simple rules above, you should get an instantaneous (but
-brief) scientific glory, possibly followed by a jail sentence. Nothing comes
-for free. Since 2015, scientific misconduct can officialy lead you to jail
+brief) scientific glory, possibly followed by jail time. Nothing comes
+for free. Since 2015, scientific misconduct can officially lead you to jail
 \citep{grant:2015}. More precisely, a former researcher has been sentenced to
@@
 your name will soon appear in the
-\href{https://en.wikipedia.org/wiki/Scientific_misconduct#Notable_individual_cases}{hall
-  of shame}.
+\href{https://en.wikipedia.org/wiki/Scientific_misconduct#Notable_individual_cases}{hall of shame}.
 

### 2017-06-28 authorea-full-article.tex
Added exported Auhorea files

\documentclass[11pt,letter]{article}

\usepackage{fullpage}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{lineno}

\usepackage{times}

\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

\renewenvironment{abstract}
  {{\bfseries\noindent{\large\abstractname}\par\nobreak}}
  {}

\renewenvironment{quote}
  {\begin{tabular}{|p{13cm}}}
  {\end{tabular}}

\titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*2}{*0.5}
\titlespacing{\subsubsection}{0pt}{*1.5}{0pt}

\usepackage{authblk}
\makeatletter
\renewcommand\AB@authnote[1]{\rlap{\textsuperscript{\normalfont#1}}}
\renewcommand\Authsep{,~\,}
\renewcommand\Authands{,~\,and }
\makeatother

\usepackage{graphicx}
\usepackage[space]{grffile}
\usepackage{latexsym}
\usepackage{textcomp}
\usepackage{longtable}
\usepackage{booktabs,array,multirow}
\usepackage{amsfonts,amsmath,amssymb}
\providecommand\citet{\cite}
\providecommand\citep{\cite}
\providecommand\citealt{\cite}
% You can conditionalize code for latexml or normal latex using this.
\newif\iflatexml\latexmlfalse
\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}%

\DeclareGraphicsExtensions{.pdf,.PDF,.png,.PNG,.jpg,.JPG,.jpeg,.JPEG}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\newcommand{\msun}{\,\mathrm{M}_\odot}

\begin{document}

\title{Ten Simple Rules for Scientific Fraud \& Misconduct}

\author[1]{Nicolas P. Rougier}%
\author[1]{john.timmer}%
\affil[1]{Affiliation not available}%

\vspace{-1em}

  \date{\today}

\begingroup
\let\center\flushleft
\let\endcenter\endflushleft
\maketitle
\endgroup

\section*{Introduction}

So, here we are! You've decided to join the dark side of Science. That's great!
You'll soon discover a brand new world of surprising results,
non-replicable experiments, fabricated data, and funny statistics. But it's not without risks: fame and shame,
retractions and lost grants, and... possibly jail. But you've made your choice, so now you need to know how to manage these risks. Only a few years ago, fraud and misconduct was a piece of
cake (See the \href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
\href{https://en.wikipedia.org/wiki/Charles_Redheffer}{Perpetual motion
  machine}, \href{https://en.wikipedia.org/wiki/Great_Moon_Hoax}{Life on Moon},
\href{https://en.wikipedia.org/wiki/Piltdown_Man}{Piltdown man},
\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). But there are lots of new players in town (\href{https://pubpeer.com}{PubPeer},
\href{http://retractionwatch.com}{RetractionWatch},
\href{https://forbetterscience.com}{For Better Science},
\href{http://blogs.discovermagazine.com/neuroskeptic/}{Neuroskeptic} to name
just a few) who have gotten pretty good at spotting and reporting fraudsters.
Furthermore, publishers have started to arm themselves with high-tech tools, and your fellow scientists are willing to name and shame you \href{https://www.youtube.com/watch?v=FXaOqwanWnU/}{on social media}. To
commit fraud or misconduct without getting caught in 2017 is a real
challenge and requires serious dedication to your task. While you'll never be smarter than an entire community of scientists, we're generously giving you some
simple rules to follow in your brand new career in fraud (see also \citep{timmer:2012}
for a set of complementary rules). Of course, neither results or (lack of) consequences are 
guaranteed.

\textbf{Disclaimer} We obviously do not encourage scientific fraud nor misconduct. The goal of this article is to alert the reader to problems that have arisen in part due to the Publish or Perish imperative, which has driven a number of researchers to cross the Rubicon without the full appreciation of the consequences. Choosing fraud will hurt science, end careers, and could have impacts on life outside of the lab. If you're tempted (even  slightly) to beautify your results, keep in mind that the benefits are probably not worth the risks.

\section*{Rule 1: Misrepresent, falsify, or fabricate your data}

In order to start your life as a scientific fraudster, the
first thing you need to do is learn how to convincingly
misrepresent, falsify, or fabricate data. If you're still hesitant about
embracing the dark side of science, you can start with a slight
misrepresentation to support your hypothesis --- a hypothesis you're sure is right anyway. Some classic techniques are
described in more detail below (see the seventh rule of \citep{rougier:2014}) but there are a number of others. If your data include numbers, there are \href{https://en.wikipedia.org/wiki/Misleading_graph}{many
  techniques} for making a graph misleading \citep{wainer:1984,raschke:2008}. If you have images, you
can change your results using
software such as Photoshop or GIMP, which allow you to change pretty
much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful, as an ever-growing number of
journals are now using forensic software to spot image manipulation
\citep{white:2007, rossner:2004,hsu:2015} (see also
\href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
  image manipulation recommendation} and \href{http://jcb.rupress.org/content/166/1/11}{Rockefeller University Press' discussion of the issue}). You can even test your whether your image has issues that could tip off an editor using the online tool \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
by Jonas Wagner. This might dissuade you from manipulating your image, but don't worry --- there are plenty of other options available to you.\\

None of the previous techniques will change the statistics of your
data, so it might be good to consider your options here. Starting with real
data, you only need to change a few points in order to take a non-significant
result and turn it into something with an astoundingly highly significance. Just see what's possible using the
\href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
\citep{schonbrodt:2015} or the interactive applet from
\citep{aschwanden:2015}. The advantage of tweaking real data is that the results  look both good and not very
suspicious. The disadvantage is that it requires some real data in the first
place, which means carrying out some actual experiments. Who wants that? Instead, you can fabricate an entire data set using software. With just a little programming skill, you can choose a correlation coefficient and X and Y mean/SD, and generate a data set with these precise
statistics \citep{matejka:2017}. (Do not pick one of the datasaurus sets because if you
plot it, it might attract the attention of an alert reader.) Whatever option you choose, make sure to
have a backup story in case people start asking about the details of the experiments. A
number of misconduct cases have been detected with just a few questions
\citep{vastag:2006}.

\section*{Rule 2: Hack your results}

If you are reluctant to manipulate your data, you still have the option of
searching through your results to find anything that reaches significance 
(a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
Significance Test)? If it's close to your field's standard one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} to report your results? Can't you use expression such as {\em nearly
  acceptable level of significance (p=0.06)}, {\em very closely brushed the
  limit of statistical significance (p=0.051)} or {\em weakly statistically
  significant (p=0.0557)}? While these statements don't make much sense, they might
be sufficient to convince a naive reviewer or reader.

If you're
suffering from a bi-polar p-value disorder, however (a term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the magical 0.05 threshold. It might be much easier than you think to portray your data as significant! The correct method for calculating the
infamous p-value is barely understood by many students, teachers, and
researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
statement to explain p's correct usage \citep{wasserstein:2016,};
Nature has issued a warning as well
\citep{baker:2016}. Consequently, before hacking your results, it might be wise
to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014}. A warning for those of you in psychology: you have to take extra-precaution because this field has drawn attention for the unusual distribution of
p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. There's now software called statcheck that can be used to recalculate the p values in your paper \citep{nuijten:2015,epskamp:2016}, making it difficult to get away with misleading statistics. Although some have called checking the results of others {\em
  methodological terrorism} \citep{finske:2016}, it might be enough to scare some away from the dark side of Science.

\section*{Rule 3: Copy/paste from others}

It's not enough to have (fake) results; you still need to publish them if you want to gain fame (and tenure, and grants). Writing is a tedious task
and can be a fair amount of work. Summarizing the state of the art in your
field will force you to actually read about what your colleagues have been doing
over the past few years. It is a very time consuming task. But in doing that reading, you may find that one of these
colleagues wrote a nice introduction to the field or a wonderful summary of its current state. If so, why bother writing a new one? It's much simpler to copy/paste what he/she has written.  Plagiarism is the nuts and bolts of scientific misconduct
\citep{neuroskeptic:2017}, be it literal copying, substantial copying or
paraphrasing (see
\href{https://www.elsevier.com/editors/perk/plagiarism-complaints}{definitions
  from Elsevier} and the committee on publication ethics' (COPE) procedure for
handle plagiarism in a
\href{https://www.elsevier.com/__data/assets/pdf_file/0005/72815/plagiarism-A.pdf}{submitted}
or
\href{https://www.elsevier.com/__data/assets/pdf_file/0020/72830/plagiarism-B_0.pdf}{published}
article).

Of course, you cannot literally take an excerpt from an
article to insert it in yours. You'd run the risk of creating a situation where the reviewer found his own text in yours. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
detection by dedicated software (e.g. iThenticate). This software is used by
universities and journals for tracking people just like you. As the databases behind these services grow, plagiarism is becoming harder and harder. Even
self-plagiarism is not allowed by a vast majority of scientific journals. All of this means that you have to be really innovative in your plagiarism techniques \citep{long:2009}. We've reached the point where writing your own text might be an easier option.

\section*{Rule 4: Write your own peer-review}

Even if you avoid all the pitfalls discussed above, you're in the clear yet. Depending on the
journal you target, you may still encounter problems with the review
process. If reviewers are picky, they may ask annoying questions,
request more information or experiments, ask for a major revision and/or reject your submission entirely. Can you imagine how this would make you feel after all your hard work
fabricating the data and plagiarized the article? There's even the risk that they'll notice your malpractice. Fortunately, there is a simple solution: write your
own review!

It is surprisingly easy to do. As you submit, you will often be asked to give name of possible reviewers. Just
provide phony names, along with email addresses that will be redirected to
your mailbox. You will soon receive an invitation to review your own work, and you're then
free to state how brilliant your own work is. Of
course, you'll have to write a review that looks like an actual review. If
you're Machiavellian, you can introduce some factual errors in your
manuscript, then report them in your review, making it look thorough. Make sure not to send you review before the deadline because as
\href{https://arstechnica.com/science/2017/04/107-cancer-papers-retracted-due-to-peer-review-fraud/}{reported
  by Elizabeth Wager} \citep{stigbrand:2017}, editors have
spotted fake reviews in part because reviewers responded promptly. Unfortunately, editors and
publishers are now aware of the scam \citep{ferguson:2014} and  have
taken counter-measures \citep{haug:2015}. For example, some of them no longer offer authors the option of recommending reviewers or if they do, the
recommendation is restricted to a list of certified reviewers. If you insist on
writing your own peer-review, you'll have to be creative and find new ways to
game the system.

\section*{Rule 5: Take advantage of predatory publishers}

If you're worried that peer review will reveal your misconduct, you still have opportunities for publishing your results. There are many predatory publishers on
the internet \citep{shen:2015}. These predators will
publish just anything
(see \href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
  Me Off Your Fucking Mailing List''} in the International Journal of Advanced
Computer Technology (2005, 2014)) and you have a 100\% chance of publication with a lighting fast review - less than 24h for some
journals. Finding a predatory publisher used to be easy thanks to a list
created and maintained by Jeffrey Beal. Although not all researchers (and publishers)
agreed with his categorization, this list provided an incredibly useful resource. Unfortunately, Beal's list was shut down just a few months ago
\citep{straumsheim:2017} and the
soon-to-be released replacement one will not be free \citep{silver:2017}. Still,
you can take advantage of the
\href{http://thinkchecksubmit.org}{Think/Check/Submit} website, which provides a
easy-to-use checklist that researchers can refer to when they are investigating
whether a journal is trustworthy. You'll obviously just want take the opposite of their sage recommendations --- like making sure \textbf{not} to pick a journal from the list of the 
\href{https://oaspa.org}{Open Access Scholarly Publishers Association} since
these journals have been thoroughly reviewed and can be trusted. Other anti-tips include finding a journal that none of your colleagues know about, looking for an editorial board that's made of
unknown or non-existent people \citep{sorokowski:2017} or dogs \citep{kennedy:2017}, and finding a publisher without any address / email / telephone number. Of course, you
will have to pay exorbitant fees to have your work published, but this is the
price to pay to have an expedited and complacent review, assuming there's any review at
all. Before making you decision where to publish, make sure to check
for the retraction fees, which may be much higher than the initial publishing
fees in some cases. But who wants to retract anyway?

\section*{Rule 6: Don't give access to your code and data}

You managed to have your article published, congratulations! You'll probably
feel a bit of a buzz, and your astonishing conclusion may draw some
newspaper headlines if your research is sexy enough. Don't get too excited about this, though. Attention means an increased chance that other researchers will start asking to access your
material, assuming the publisher has not already requested it prior to
publication. Of course, that's very bad news for you if your data
has been fabricated or if your statistical analysis is not really academic. You definitely cannot give others access to your raw if it doesn't exist! Fortunately, researchers have been avoiding sharing their data for decades, and the same old
reasons still apply
\citep{roche:2014}: ``Oh you know, my data cannot be anonymized''; ``You
would not understand the structure of my data''; ``A lot of money has been
invested, I cannot give it for free''; etc. You can even tell anyone
asking for your data that they are {\em a research parasite} \citep{longo:2016}
although that approach seems to have drawn some unwanted attention
(\url{http://researchparasite.com}).  Technological excuses might also be worth
a try. When \citep{collberg:2014,collberg:2015} tried to access the code used in
several publications, they get some really great answers: ``Too busy to help'';
``Code will be available soon''; ``Bad backup practice''; etc. Just pick one
you like. With the increasing pressure by funding bodies (NIH, NSF,
Europe, etc) to share data, it might be good to pretend (and only pretend) to be a
supporter of Open Data by inserting a simple ``data available upon request'' or
``data is available from my website''. This does not come close to meeting the
FAIR principles (findable, accessible, inter-operable, re-usable,
\cite{wilkinson:2016}), but who cares if you can give the illusion you're not
afraid of sharing your data? Don't get us wrong, though - you will never answer a
request, and the data will never appear on your website.

\section*{Rule 7: Do not allow for replication outside your lab}

Here comes the tricky part: replication. It may surprise you, but some researchers
may want to replicate your results using the methods explained in your
article. \citep{nosek:2015} replicated 100 experiments reported in three high-ranking psychology journal. Or tried, at least; they
concluded that some experiments were not replicable at all. There are even scientific journals that are now dedicated to replications
(e.g. \url{http://rescience.github.io}).

If people try to replicate your work
and do not get the same results, you have a problem. They may insist on seeing your actual
data and, if you refuse, you might be suspected of
fraud or misconduct. You can try rule 6, but if there are several failed replications, it will be much
harder to deny access to your data. One easy way to avoid this sort of disaster is
to claim in your article that the experiment/study has been already
replicated in your lab. The subliminal message to the reader is ``Don't bother
to replicate this, we've already taken care of that and it works, believe us. Don't
waste your time, you will thank us later''. If this doesn't work, you can also
try issuing a {\em Do Not Replicate order} as proposed by
\href{https://mchankins.wordpress.com/2014/07/12/do-not-replicate/}{Matthew
  Hankins} (who is kind enough as to provide a template). It is not yet widely
used , but with the replication crisis we're facing, we're confident it will soon become popular.

\section*{Rule 8: Never, ever, retract your results}

If you've made a genuine (and big) mistake in your work, there is no problem in
asking for the retraction of your paper  \citep{miller:2006}. It's a
behavior that is actually rewarded according to \citep{lu:2013} (positive citation benefits for prior work), even though in some cases, it can take several years \citep{trivers:2009}. However, if you've been
engaged in fraud, having your paper retracted is like an admission of guilt. It's something to be avoided. Retraction could start with a simple comment to the
editor saying there may be a problem with you paper. If you're lucky, the comment will never be published
\citep{trebino:2009}. Otherwise, you'll have to give a convincing answer, or the editor could decide to retract your paper
without your consent. So it's critical to act quickly, defusing the crisis with a simple corrigendum admitting a bad - but not fatal - error during preparation of the publication.  Don't hesitate to publish as many corrigendum as
necessary to make critics happy. You can drag this out for several years, which is hopefully enough time for people to forget about the issues.

\section*{Rule 9: Don't get caught. Deny if caught.}

If you intend to persist in a rogue scientific career, you have to be aware that
you're likely to get caught sooner or later. The number of researcher to have never been caught is probably low; only the best can hope to be caught only after their death
\citep{degroote:2016,}. But being caught while you're still breathing does not mean you career will come to
an end. There is a set of simple rules to follow if you need to deny scientific misconduct:
\begin{itemize}
  \item If you're first author, explain you were supervised by the last author and
    had no choice.
  \item If you're last author, explain you were not aware of the misconduct of
    the first author.
  \item If your name is not first nor last, claim that you didn't even know your
    name appeared in the publication.
  \item If your name appears because of {\em gift authorship}, just admit it.
    It might be considered misconduct, but fraud is much worse.
  \item The intern, who cannot be contacted because he/she left academia, is
    responsible for everything
  \item Send threatening letters to those who have spotted your misconduct
  \item Follow through on those threats and sue'em all
\end{itemize}
If you're lucky enough, one of the above will work and things should be back to
normal. All of this is easier, of course, if you're supported by you employer because you've been
labeled a rising star.

\section*{Rule 10: Be creative (for once)}

If you look at the annual list of
\href{http://www.the-scientist.com/?articles.view/articleNo/47813/title/Top-10-Retractions-of-2016/}{top
  ten retractions} compiled by Adam Marcus and Ivan Oransky (co-founders of the
RetractionWatch), you'll realize that all the tactics mentioned above are
already quite well known by the research community. If you want to stay off the radar
while committing fraud and misconduct, you'll want to be creative and invent
your own rules.

\section*{Conclusion}

By following the simple rules above, you should get scientific glory if only temporarily. The downside is that it could be followed by jail time \citep{grant:2015}. A former researcher has been sentenced to
57 months jail and to pay-back 7.2 millions dollars. Science has been and is
still poisoned by fraud and misconduct, but it is now fighting back with increasingly high-tech tools \citep{buranyi:2017}. Today, the risks that come when you engage in
fraud and misconduct are really high, and the chances of being
caught have gone up. So you'd better think twice before committing misconduct, or
your name will soon appear in Wikipedia's
\href{https://en.wikipedia.org/wiki/Scientific_misconduct#Notable_individual_cases}{hall of shame}.

\selectlanguage{english}
\bibliographystyle{unsrt}
\bibliography{bibliography/converted_to_latex.bib%
}

\end{document}

### 2017-06-28 article.tex
First complete draft with John Timmer

@@
 \rhead{\footnotesize \sf \today}
-\lhead{\footnotesize \sf NP Rougier \textbullet~Ten Simple Rules for Fraud \& Misconduct}
+\lhead{\footnotesize \sf Rougier \& Timmer \textbullet~Ten Simple Rules for Scientific Fraud \& Misconduct}
 \rfoot{\footnotesize \sf \thepage}
@@
 
-\title{Ten Simple Rules for Fraud \& Misconduct}
+\title{\Large Ten Simple Rules for Scientific Fraud \& Misconduct}
 \author{%
-  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$\\
+  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$ \textbf{and John Timmer}$^{4}$\\
   \begin{footnotesize}
@@
     $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
-          CNRS, UMR 5800, Talence, France\\
+          CNRS, UMR 5800, Talence, France
+    $^{4}$Ars Technica, Condé Nast, New York, NY, USA\\
     $^{*}$Corresponding author:
@@
 \begin{small}
-\noindent {\sf \textbf{Disclaimer.} We do not encourage scientific fraud nor
-  misconduct. The goal of this provocative article is to alert the reader on a
-  preoccupying situation in Science. Facing the Publish or Perish alternative,
-  a number of researchers have decided to cross the Rubicon without the full
-  knowledge of the dramatic consequences that may hurt Science and impact not
-  only their scientific life but their actual life as well. If you're tempted
-  to (even so slightly) beautify your results, keep in mind that the game is
-  probably not worth the risks.}\par
+  \noindent {\sf \textbf{Disclaimer.} We obviously do not encourage scientific
+    fraud nor misconduct. The goal of this article is to alert the reader to
+    problems that have arisen in part due to the Publish or Perish imperative,
+    which has driven a number of researchers to cross the Rubicon without the
+    full appreciation of the consequences. Choosing fraud will hurt science,
+    end careers, and could have impacts on life outside of the lab. If you're
+    tempted (even slightly) to beautify your results, keep in mind that the
+    benefits are probably not worth the risks.}\par
 \end{small}
@@
 So, here we are! You've decided to join the dark side of Science. That's great!
-You'll soon discover a brand new world of shiny and surprising results,
-non-replicable experiments, fabricated data, funny statistics, fame and shame,
-joy and sadness, and... jail. But you've made your choice (for whatever
-reasons) and you better have to be well prepared because Science is strong on
-the other side. Only a few years from now, fraud and misconduct was a piece of
-cake (\href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
+You'll soon discover a brand new world of surprising results,
+non-replicable experiments, fabricated data, and funny statistics. But it's not without risks: fame and shame,
+retractions and lost grants, and... possibly jail. But you've made your choice, so now you need to know how to manage these risks. Only a few years ago, fraud and misconduct was a piece of
+cake (See the \href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
 \href{https://en.wikipedia.org/wiki/Charles_Redheffer}{Perpetual motion
@@
 \href{https://en.wikipedia.org/wiki/Piltdown_Man}{Piltdown man},
-\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). Problem is
-that there are new players in town (\href{https://pubpeer.com}{PubPeer},
+\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). But there are lots of new players in town (\href{https://pubpeer.com}{PubPeer},
 \href{http://retractionwatch.com}{RetractionWatch},
@@
 \href{http://blogs.discovermagazine.com/neuroskeptic/}{Neuroskeptic} to name
-just a few) and they're pretty good at spotting and reporting fraudsters.
-Furthermore, publishers have started to retaliate with high-tech tools. To
-commit fraud or misconduct without getting caught in 2017 is kind of a
-challenge and requires a real dedication to your task. But there will be always
-people that think they're smarter than a whole community. And because we love
-to have things done in the proper way, we're kind enough to give you some
-simple rules to follow in your brand new career (see also \citep{timmer:2012}
-for a set of complementary rules). However, results and consequences are not
+just a few) who have gotten pretty good at spotting and reporting fraudsters.
+Furthermore, publishers have started to arm themselves with high-tech tools, and your fellow scientists are willing to name and shame you \href{https://www.youtube.com/watch?v=FXaOqwanWnU/}{on social media}.
+To
+commit fraud or misconduct without getting caught in 2017 is a real
+challenge and requires serious dedication to your task. While you'll never be smarter than an entire community of scientists, we're generously giving you some
+simple rules to follow in your brand new career in fraud (see also \citep{timmer:2012}
+for a set of complementary rules). Of course, neither results or (lack of) consequences are 
 guaranteed.
 
-\section*{Rule 1: Misrepresent, falsify or fabricate your data}
+\section*{Rule 1: Misrepresent, falsify, or fabricate your data}
 
-In order to start a plain and deceitful scientific fraudster life, the very
-first thing you need to gain expertise on is to learn how to convincingly
-misrepresent, falsify or fabricate your data. If you're still hesitating at
-embracing the dark side of Science, you may start with a slight
-mis-representation to strengthen your hypothesis. Some classical techniques are
-illustrated in the seventh rule of \citep{rougier:2014} but there are
-actually \href{https://en.wikipedia.org/wiki/Misleading_graph}{many more
-  techniques} to make a graph misleading \citep{wainer:1984,raschke:2008}. You
-can also directly change your results in a post-production phase by using
-software such as Photoshop or Gimp that makes it really easy to change pretty
-much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful
-of not making too obvious manipulations because an ever-growing number of
-journals are now equipped with forensic software to spot image manipulation
+In order to start your life as a scientific fraudster, the
+first thing you need to do is learn how to convincingly
+misrepresent, falsify, or fabricate data. If you're still hesitant about
+embracing the dark side of science, you can start with a slight
+misrepresentation to support your hypothesis --- a hypothesis you're sure is right anyway. Some classic techniques are
+described in more detail below (see the seventh rule of \citep{rougier:2014}) but there are a number of others.
+If your data include numbers, there are \href{https://en.wikipedia.org/wiki/Misleading_graph}{many
+  techniques} for making a graph misleading \citep{wainer:1984,raschke:2008}. If you have images, you
+can change your results using
+software such as Photoshop or GIMP, which allow you to change pretty
+much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful, as an ever-growing number of
+journals are now using forensic software to spot image manipulation
 \citep{white:2007, rossner:2004,hsu:2015} (see also
 \href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
-  image manipulation recommendation}). You can even test your image online
-using \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
-by Jonas Wagner. This should dissuade you from manipulating your image by
-yourself.
-%
-%% \begin{wrapfigure}{r}{0.4\textwidth}
-%% %  \vspace{-8mm}
-%%   \begin{center}
-%%     \includegraphics[width=0.4\textwidth]{datasaurus}
-%%   \end{center}
-%%   \caption{The Datasaurus set by \href{http://www.thefunctionalart.com/2016/08/download-datasaurus-never-trust-summary.html}{Alberto Cairo}. }
-%%   \label{fig:datasaurus}
-%% \end{wrapfigure}
-%
-Furthermore, none of the previous techniques will change the statistics of your
-data and it might a better choice to falsify your data. Starting with real
-data, you can change only a few points in order to change a non-significant
-results into an astoundingly highly significant result as shown on the
+  image manipulation recommendation} and \href{http://jcb.rupress.org/content/166/1/11}{Rockefeller University Press' discussion of the issue}).
+You can even test your whether your image has issues that could tip off an editor using the online tool \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
+by Jonas Wagner. This might dissuade you from manipulating your image, but don't worry --- there are plenty of other options available to you.\\
+
+None of the previous techniques will change the statistics of your
+data, so it might be good to consider your options here. Starting with real
+data, you only need to change a few points in order to take a non-significant
+result and turn it into something with an astoundingly highly significance. Just see what's possible using the
 \href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
 \citep{schonbrodt:2015} or the interactive applet from
-\citep{aschwanden:2015}. The advantage of falsifying real data is that changing
-only a few points will still make your data looks good and not too much
+\citep{aschwanden:2015}. The advantage of tweaking real data is that the results  look both good and not very
 suspicious. The disadvantage is that it requires some real data in the first
-place and thus it requires to carry on some actual experiment (i.e. some
-work). As a last resort, you can also fabricate the whole data set using a
-specific program. For example, starting from a given X mean/SD, Y mean/SD, and
-a correlation coefficient, you can generate a data set with these precise
-statistics \citep{matejka:2017}. Do not pick the datasaurus set because if you
-plot it, it might look suspicious for the alert reader. Finally, make sure to
-have a backup story when people will start asking or investigating
-how/when/where/how did you do perform the experiments to get these data. A
-number of misconducts have been detected after just a few questions
+place, which means carrying out some actual experiments.
+Who wants that?
+Instead, you can fabricate an entire data set using software.
+With just a little programming skill, you can choose a correlation coefficient and X and Y mean/SD, and generate a data set with these precise
+statistics \citep{matejka:2017}. (Do not pick one of the datasaurus sets because if you
+plot it, it might attract the attention of an alert reader.) Whatever option you choose, make sure to
+have a backup story in case people start asking about the details of the experiments. A
+number of misconduct cases have been detected with just a few questions
 \citep{vastag:2006}.
@@
 
-%% \begin{wrapfigure}{l}{0.4\textwidth}
-%%   \vspace{-5mm}
-%%   \begin{center}
-%%     \includegraphics[width=0.4\textwidth]{xkcd}
-%%   \end{center}
-%%   \caption{P-Values by XKCD (\url{https://xkcd.com/1478/}). This work is
-%%     licensed under a CC-BY-NC 2.5 License.}
-%%   \label{fig:xkcd}
-%% \end{wrapfigure}
-If you are reluctant at manipulating your data, you still have the option of
-simply hacking your results in order to reach the significance level
-(a.k.a. p-hacking). But before committing any scientific misconduct, are you
-sure you need to do so? What is the p value of your NHST (Null Hypothesis
-Significance Test)? Did you consider using one of the many qualification
+If you are reluctant to manipulate your data, you still have the option of
+searching through your results to find anything that reaches significance 
+(a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
+Significance Test)? If it's close to your field's standard one of the many qualification
 proposed by
@@
   limit of statistical significance (p=0.051)} or {\em weakly statistically
-  significant (p=0.0557)}? It does not make sense, but in some cases, it might
-be sufficient to convince a naive reviewer or reader. However, if you're
-suffering from a bi-polar p-value disorder (term coined by
+  significant (p=0.0557)}? While these statements don't make much sense, they might
+be sufficient to convince a naive reviewer or reader.
+
+If you're
+suffering from a bi-polar p-value disorder, however (a term coined by
 \href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
-  Lakens}), you'll want to reach the magical 0.05 threshold and it might
-actually be much easier than you think because the correct usage of the
-infamous p-value is hardly understood by a number of students, teachers or
-researchers \citep{haller:2002,lecoutre:2003}. The current situation is
-actually so bad that the American Statistical Association had to release a
-statement to explain the correct usage \citep{wasserstein:2016,} last year and
-Nature has issued as well some warning on the usage of the p-value
+  Lakens}), you'll want to reach the magical 0.05 threshold. It might be much easier than you think to portray your data as significant! The correct method for calculating the
+infamous p-value is barely understood by many students, teachers, and
+researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
+statement to explain p's correct usage \citep{wasserstein:2016,};
+Nature has issued a warning as well
 \citep{baker:2016}. Consequently, before hacking your results, it might be wise
 to re-read your classics
-\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014} if you want to
-take full advantage of the misuse of p-value. Last, but not least, if you're in
-psychology, you have to take extra-precaution because this domain has recently
-raised concerns, especially when it comes to the unusual distribution of
-p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. If you add the
-statcheck variable into the equation \citep{nuijten:2015,epskamp:2016}, it
-might be difficult to achieve a proper p-hacking of your results without being
-noticed. Even though some people would call such results checking {\em
-  methodological terrorism} \citep{finske:2016}, it might be time to reconsider
-your commitment to the dark side of Science.
+\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014}.
+A warning for those of you in psychology: you have to take extra-precaution because this field has drawn attention for the unusual distribution of
+p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}.
+There's now software called statcheck that can be used to recalculate the p values in your paper \citep{nuijten:2015,epskamp:2016}, making it difficult to get away with misleading statistics.
+Although some have called checking the results of others {\em
+  methodological terrorism} \citep{finske:2016}, it might be enough to scare some away from the dark side of Science.
 
@@
 
-You have your (fake) results but you still need to publish your clickbait
-article to gain fame (and tenure and professorship). Writing is a tedious task
-and might represent a fair amount of work. Writing the state of the art in your
-domain requires to actually read (what?) what your colleagues have been doing
-over the past few years. It is a very time consuming task. But if one of these
-colleagues wrote a nice introduction to the domain or a wonderful state of the
-art, why bother writing a new one? Why not copy/paste what he/she has written
-instead?  Plagiarism is the nuts and bolts of scientific misconduct
+It's not enough to have (fake) results; you still need to publish them if you want to gain fame (and tenure, and grants). Writing is a tedious task
+and can be a fair amount of work. Summarizing the state of the art in your
+field will force you to actually read about what your colleagues have been doing
+over the past few years. It is a very time consuming task. But in doing that reading, you may find that one of these
+colleagues wrote a nice introduction to the field or a wonderful summary of its current state.
+If so, why bother writing a new one?
+It's much simpler to copy/paste what he/she has written.
+Plagiarism is the nuts and bolts of scientific misconduct
 \citep{neuroskeptic:2017}, be it literal copying, substantial copying or
@@
 \href{https://www.elsevier.com/editors/perk/plagiarism-complaints}{definitions
-  from Elsevier} and the committee on publication ethics (COPE) procedure to
+  from Elsevier} and the committee on publication ethics' (COPE) procedure for
 handle plagiarism in a
@@
 \href{https://www.elsevier.com/__data/assets/pdf_file/0020/72830/plagiarism-B_0.pdf}{published}
-article). Of course, you cannot literally copy paste an excerpt of text from an
-article to insert it in yours. Just imagine a situation where the reviewer
-would also be the author of the text being reviewed. Consequently, if you
+article).
+
+Of course, you cannot literally take an excerpt from an
+article to insert it in yours. You'd run the risk of creating a situation where the reviewer found his own text in yours. Consequently, if you
 really intend to plagiarize, you'll need to transform the text drastically to
 avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
-detection by dedicated software (e.g. iThenticate). These software are used by
-universities and journals for tracking people just like you. And since their
-database is really huge, plagiarism is harder and harder. Can you imagine than
-self-plagiarism is not even allowed for a vast majority of journals? In the
-end, you really have to improve or innovate in your techniques and to work very
-hard \citep{long:2009}. But faced with such an adversarial nature of the
-situation, to write your very own text might be an easier option.
+detection by dedicated software (e.g. iThenticate). This software is used by
+universities and journals for tracking people just like you. As the databases behind these services grow, plagiarism is becoming harder and harder. Even
+self-plagiarism is not allowed by a vast majority of scientific journals.
+All of this means that you have to be really innovative in your plagiarism techniques \citep{long:2009}.
+We've reached the point where writing your own text might be an easier option.
 
@@
 
-%% \begin{wrapfigure}{r}{0.5\textwidth}
-%%   \vspace{-5mm}
-%%   \begin{center}
-%%     \includegraphics[width=0.5\textwidth]{phd-comics}
-%%   \end{center}
-%%   \caption{Addressing reviewers comments. PhD Comics
-%%     (\url{http://phdcomics.com}). Copyright (c) 2005 Jorge Cham.}
-%% \end{wrapfigure}
+Even if you avoid all the pitfalls discussed above, you're in the clear yet. Depending on the
+journal you target, you may still encounter problems with the review
+process. If reviewers are picky, they may ask annoying questions,
+request more information or experiments, ask for a major revision and/or reject your submission entirely. Can you imagine how this would make you feel after all your hard work
+fabricating the data and plagiarized the article? There's even the risk that they'll notice your malpractice. Fortunately, there is a simple solution: write your
+own review!
 
-Results and papers are ready and it is now time to submit. Depending on the
-journal you target, you may still encounter some problem with the review
-process. If reviewers are a bit too picky, they may ask you annoying questions,
-be a bit suspicious, request more information, ask for a major revision and or
-even reject your submission (can you imagine?). After all your hard work at
-fabricating the data and plagiarized the article, that would be really
-unfair. Fortunately, there is a simple solution. You can actually write your
-own review! How is that possible you may ask? It is incredibly easy. At the
-time of submission, you will be asked to give name of possible reviewers, just
-give phony names with corresponding email addresses that will be redirected to
-your mailbox. You will soon receive an invitation to review and you're then
-free to write your own review and state how brilliant is your own work. Of
+It is surprisingly easy to do. As you submit, you will often be asked to give name of possible reviewers. Just
+provide phony names, along with email addresses that will be redirected to
+your mailbox. You will soon receive an invitation to review your own work, and you're then
+free to state how brilliant your own work is. Of
 course, you'll have to write a review that looks like an actual review. If
-you're Machiavellian, you will have introduced some factual errors in your
-manuscript such that you can report them later in your review. Make sure also
-to not send you review before the editor deadline because as
+you're Machiavellian, you can introduce some factual errors in your
+manuscript, then report them in your review, making it look thorough. Make sure not to send you review before the deadline because as
 \href{https://arstechnica.com/science/2017/04/107-cancer-papers-retracted-due-to-peer-review-fraud/}{reported
-  by Elizabeth Wager} \citep{stigbrand:2017}, one of the reasons the editors
-spotted fake reviews was that reviewers responded just in time. However, editors and
-publishers are now well aware of the scam \citep{ferguson:2014} and they have
-taken counter-measures \citep{haug:2015}. For example, some of them do not offer
-anymore the option to recommend unknown reviewer or if they do, the
+  by Elizabeth Wager} \citep{stigbrand:2017}, editors have
+spotted fake reviews in part because reviewers responded promptly. Unfortunately, editors and
+publishers are now aware of the scam \citep{ferguson:2014} and  have
+taken counter-measures \citep{haug:2015}. For example, some of them no longer offer authors the option of recommending reviewers or if they do, the
 recommendation is restricted to a list of certified reviewers. If you insist on
@@
 
-If most journals will most likely reject your submission because you've applied
-some of the rules above and get caught red-handed, you still have opportunities
-to publish your results in one of the many predatory publishers available on
-the internet and the internet only \citep{shen:2015}. Such predators will
+If you're worried that peer review will reveal your misconduct, you still have opportunities for publishing your results. There are many predatory publishers on
+the internet \citep{shen:2015}. These predators will
 publish just anything
-(\href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
+(see \href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
   Me Off Your Fucking Mailing List''} in the International Journal of Advanced
-Computer Technology (2005, 2014)) and you have a 100\% chance to have your
-article published with a lighting fast review, less than 24h for some
-journals. Finding a predatory publisher used to be easy thanks to the list
-created and maintained by Jeffrey Beal. Even if some people (and publishers)
-have judged this list to be controversial, it was incredibly useful for a lot
-of people. Unfortunately, this list has closed just a few months ago
+Computer Technology (2005, 2014)) and you have a 100\% chance of publication with a lighting fast review - less than 24h for some
+journals. Finding a predatory publisher used to be easy thanks to a list
+created and maintained by Jeffrey Beal. Although not all researchers (and publishers)
+agreed with his categorization, this list provided an incredibly useful resource. Unfortunately, Beal's list was shut down just a few months ago
 \citep{straumsheim:2017} and the
-soon-to-be released replacement one will not be free \citep{silver:2017}. But
-you can now take advantage of the
-\href{http://thinkchecksubmit.org}{Think/Check/Submit} website that provides a
+soon-to-be released replacement one will not be free \citep{silver:2017}. Still,
+you can take advantage of the
+\href{http://thinkchecksubmit.org}{Think/Check/Submit} website, which provides a
 easy-to-use checklist that researchers can refer to when they are investigating
-whether a journal can be trusted. Just take the opposite of their wise
-recommendations and make sure to \textbf{not} pick a journal from the list
+whether a journal is trustworthy. You'll obviously just want take the opposite of their sage recommendations --- like making sure \textbf{not} to pick a journal from the list of the 
 \href{https://oaspa.org}{Open Access Scholarly Publishers Association} since
-these journals have been thoroughly reviewed and can be trusted. For example,
-if none of your colleagues know the journal, if the editorial board is made of
-unknown or non-existent people \citep{sorokowski:2017} or even dogs in some
-cases \citep{kennedy:2017} and no address / email / telephone is provided to
-contact the publisher, you may have knocked at the right door. Of course, you
+these journals have been thoroughly reviewed and can be trusted. Other anti-tips include finding a journal that none of your colleagues know about, looking for an editorial board that's made of
+unknown or non-existent people \citep{sorokowski:2017} or dogs \citep{kennedy:2017}, and finding a publisher without any address / email / telephone number. Of course, you
 will have to pay exorbitant fees to have your work published, but this is the
-price to pay to have an expedited and complaisant review, if any review at
-all. Before making you decision where to publish, make sure to check as well
-for the retraction fees that may be much higher than the initial publishing
+price to pay to have an expedited and complacent review, assuming there's any review at
+all. Before making you decision where to publish, make sure to check
+for the retraction fees, which may be much higher than the initial publishing
 fees in some cases. But who wants to retract anyway?
@@
 
-%% \begin{wrapfigure}{l}{0.4\textwidth}
-%%   \vspace{-6mm}
-%%   \begin{center}
-%%     \includegraphics[width=0.4\textwidth]{data-share}
-%%   \end{center}
-%%   \caption{Image by Ainsley Seago.}
-%%   \label{fig:datasaurus}
-%% \end{wrapfigure}
-
 You managed to have your article published, congratulations! You'll probably
-get a lot of buzz and maybe your amazing conclusion will make it to the
-newspaper headlines if your research is sexy enough. Because of the buzz,
-chances are increased that people will start asking you to access your
-material, if the publisher has not already requested it prior to
-publication. Of course, that's quite a bad news for you because if your data
-has been fabricated or if your statistical analysis is not really academic,
-your colleagues might discover your misconduct. Consequently, you definitely
-cannot give access to your raw material. For this, you can use the same old
-reasons that have prevented data sharing for a very long time
-\citep{roche:2014}: ``Oh you know, my data cannot be anonymized'', ``No, you
-would not understand the structure of my data'', ``A lot of money has been
-invested, I cannot give it for free'', etc. You can also tell these people
-asking for your data that they are {\em research parasites} \citep{longo:2016}
-even though the techniques seems to have backfired since then
+feel a bit of a buzz, and your astonishing conclusion may draw some
+newspaper headlines if your research is sexy enough. Don't get too excited about this, though. Attention means an increased chance that other researchers will start asking to access your
+material, assuming the publisher has not already requested it prior to
+publication. Of course, that's very bad news for you if your data
+has been fabricated or if your statistical analysis is not really academic.
+You definitely cannot give others access to your raw if it doesn't exist!
+Fortunately, researchers have been avoiding sharing their data for decades, and the same old
+reasons still apply
+\citep{roche:2014}: ``Oh you know, my data cannot be anonymized''; ``You
+would not understand the structure of my data''; ``A lot of money has been
+invested, I cannot give it for free''; etc. You can even tell anyone
+asking for your data that they are {\em a research parasite} \citep{longo:2016}
+although that approach seems to have drawn some unwanted attention
 (\url{http://researchparasite.com}).  Technological excuses might also be worth
-a try. When \citep{collberg:2014,collberg:2015} tried to access the code of
-several publications, they get some really great answers ``Too busy to help'',
-``Code will be available soon'', ``Bad backup practice'', etc. Just pick one
-you like. Finally, with the increasing pressure by institutions (NIH, NSF,
-Europe, etc) to share data, you can pretend (and only pretend) to be a
+a try. When \citep{collberg:2014,collberg:2015} tried to access the code used in
+several publications, they get some really great answers: ``Too busy to help'';
+``Code will be available soon''; ``Bad backup practice''; etc. Just pick one
+you like. With the increasing pressure by funding bodies (NIH, NSF,
+Europe, etc) to share data, it might be good to pretend (and only pretend) to be a
 supporter of Open Data by inserting a simple ``data available upon request'' or
-``data is available from my website''. This does not correspond at all to the
+``data is available from my website''. This does not come close to meeting the
 FAIR principles (findable, accessible, inter-operable, re-usable,
-\cite{wilkinson:2016}), but who cares if you can give the illusion to not be
-afraid of sharing your data? But don't get me wrong, you will never answer a
+\cite{wilkinson:2016}), but who cares if you can give the illusion you're not
+afraid of sharing your data? Don't get us wrong, though - you will never answer a
 request, and the data will never appear on your website.
@@
 
-Here comes the tricky part: replications. Can you imagine that some researchers
-are willing to replicate your results based on what you've explained in your
-article? \citep{nosek:2015} replicated 100 experiments reported in papers
-published in three high-ranking psychology journal. And of course, they
-concluded that some experiments were not replicable at all. How surprising!
-Even worse, there is now scientific journals dedicated to replications
-(e.g. \url{http://rescience.github.io}). If people start to replicate your work
-and do not get the same results, you have a problem. You might be suspected of
-fraud or misconduct and people will really insist on seeing you actual
-data. You can try rule 6, but after several failed replication, it will be much
-harder to deny access to your data. One easy way to avoid imminent disaster is
-to claim beforehand in your article that the experiment/study has been already
+Here comes the tricky part: replication. It may surprise you, but some researchers
+may want to replicate your results using the methods explained in your
+article. \citep{nosek:2015} replicated 100 experiments reported in three high-ranking psychology journal. Or tried, at least; they
+concluded that some experiments were not replicable at all. There are even scientific journals that are now dedicated to replications
+(e.g. \url{http://rescience.github.io}).
+
+If people try to replicate your work
+and do not get the same results, you have a problem. They may insist on seeing your actual
+data and, if you refuse, you might be suspected of
+fraud or misconduct. You can try rule 6, but if there are several failed replications, it will be much
+harder to deny access to your data. One easy way to avoid this sort of disaster is
+to claim in your article that the experiment/study has been already
 replicated in your lab. The subliminal message to the reader is ``Don't bother
-to replicate, we've already taken care of that and it works, believe us. Don't
-lose your time, you will thank us later''. If this doesn't work, you can also
-try a {\em Do Not Replicate order} as proposed by
+to replicate this, we've already taken care of that and it works, believe us. Don't
+waste your time, you will thank us later''. If this doesn't work, you can also
+try issuing a {\em Do Not Replicate order} as proposed by
 \href{https://mchankins.wordpress.com/2014/07/12/do-not-replicate/}{Matthew
   Hankins} (who is kind enough as to provide a template). It is not yet widely
-used yet, but with the replication crisis we're facing in several scientific
-domain, we're confident it will soon become popular.
+used , but with the replication crisis we're facing, we're confident it will soon become popular.
 
@@
 If you've made a genuine (and big) mistake in your work, there is no problem in
-asking for the retraction of your paper \citep{miller:2006}. This is actually a
-behavior that is rewarded according to \citep{lu:2013}, even though in some
-cases, it can take several years \citep{trivers:2009}. However, if you've been
-frauding, having your paper retracted is like an admission of fraud and you
-want to avoid that. Such retraction may start with a simple comment to the
-editor saying there may be some problem with you paper. If you're lucky, such
-comment, even if sound, will never make it into the journal
-\citep{trebino:2009}, else, you'll have to give a convincing answer. Depending
-how you addressed the comment, the editor can decide to retract your paper even
-without your consent. Before reaching this failure climax, you better have to
-start with a simple corrigendum pretexting a bad preparation of the material
-for the publication.  Don't hesitate to publish as many corrigendum as
-necessary to make critics happy. This can last for several years, the time
-needed for people to forget about your fraud or misconduct.
+asking for the retraction of your paper  \citep{miller:2006}. It's a
+behavior that is actually rewarded according to \citep{lu:2013} (positive citation benefits for prior work), even though in some cases, it can take several years \citep{trivers:2009}.
+However, if you've been
+engaged in fraud, having your paper retracted is like an admission of guilt. It's something to be avoided. Retraction could start with a simple comment to the
+editor saying there may be a problem with you paper. If you're lucky, the comment will never be published
+\citep{trebino:2009}. Otherwise, you'll have to give a convincing answer, or the editor could decide to retract your paper
+without your consent.
+So it's critical to act quickly, defusing the crisis with a simple corrigendum admitting a bad - but not fatal - error during preparation of the publication.
+Don't hesitate to publish as many corrigendum as
+necessary to make critics happy. You can drag this out for several years, which is hopefully enough time for people to forget about the issues.
 
@@
 
-If you intend to persist in your rogue scientific career, you have to know that
-most likely, you'll get caught. The sooner or the later, but it will happen
-eventually. The number of researcher to have never been caught is extremely low
-and only the best can hope to be caught only after their death
-\citep{degroote:2016,}. But being caught does not mean you career will come to
-an end. There is actually a set of simple rules to deny having committed any
-scientific misconduct:
+If you intend to persist in a rogue scientific career, you have to be aware that
+you're likely to get caught sooner or later. The number of researcher to have never been caught is probably low; only the best can hope to be caught only after their death
+\citep{degroote:2016,}. But being caught while you're still breathing does not mean you career will come to
+an end. There is a set of simple rules to follow if you need to deny scientific misconduct:
 \begin{itemize}
-  \item If you're first author, explain you were supervised by last author and
+  \item If you're first author, explain you were supervised by the last author and
     had no choice.
@@
     the first author.
-  \item If your name is not first nor last, explain you did not even know your
+  \item If your name is not first nor last, claim that you didn't even know your
     name appeared in the publication.
-  \item If your name appears because of {\em gift authorship}, just say it.
+  \item If your name appears because of {\em gift authorship}, just admit it.
     It might be considered misconduct, but fraud is much worse.
-  \item The intern, that cannot be contacted because he/she left academia is
+  \item The intern, who cannot be contacted because he/she left academia, is
     responsible for everything
-  \item Send threat letter to those who have spotted your misconduct
-  \item Sue'em all
+  \item Send threatening letters to those who have spotted your misconduct
+  \item Follow through on those threats and sue'em all
 \end{itemize}
-If you're lucky enough, any of the above will do and things should be back to
-normal, especially if you're supported by you employer because you've been
-labeled as a rising star.
+If you're lucky enough, one of the above will work and things should be back to
+normal. All of this is easier, of course, if you're supported by you employer because you've been
+labeled a rising star.
 
@@
 
-If you look at the yearly list of
+If you look at the annual list of
 \href{http://www.the-scientist.com/?articles.view/articleNo/47813/title/Top-10-Retractions-of-2016/}{top
   ten retractions} compiled by Adam Marcus and Ivan Oransky (co-founders of the
-RetractionWatch) since 2012, you'll realize that all the above rules are
-already quite well known in the community. If you want to stay off the radar
-while committing fraud and misconduct, you'll have to be creative and invent
-new rules.
+RetractionWatch), you'll realize that all the tactics mentioned above are
+already quite well known by the research community. If you want to stay off the radar
+while committing fraud and misconduct, you'll want to be creative and invent
+your own rules.
 
@@
 
-By following the simple rules above, you should get an instantaneous (but
-brief) scientific glory, possibly followed by jail time. Nothing comes
-for free. Since 2015, scientific misconduct can officially lead you to jail
-\citep{grant:2015}. More precisely, a former researcher has been sentenced to
+By following the simple rules above, you should get scientific glory if only temporarily.
+The downside is that it could be followed by jail time \citep{grant:2015}.
+A former researcher has been sentenced to
 57 months jail and to pay-back 7.2 millions dollars. Science has been and is
-still poisoned by fraud and misconduct, but it is now fighting back and the
-high-tech war has begun \citep{buranyi:2017}. Today, the risks associated with
-fraud and misconduct are really high as well as the chances of being
-caught. Consequently, you'd better think twice before committing misconduct or
-your name will soon appear in the
+still poisoned by fraud and misconduct, but it is now fighting back with increasingly high-tech tools \citep{buranyi:2017}. Today, the risks that come when you engage in
+fraud and misconduct are really high, and the chances of being
+caught have gone up. So you'd better think twice before committing misconduct, or
+your name will soon appear in Wikipedia's
 \href{https://en.wikipedia.org/wiki/Scientific_misconduct#Notable_individual_cases}{hall of shame}.

### 2017-07-24 article.tex
Typo
Update

@@
     \node[xshift=-2.85cm,yshift=-2.85cm] at (current page.north east) {
-        \includegraphics[width=3cm]{stample}
+        \includegraphics[width=3cm]{stample.pdf}
     };
@@
 (a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
-Significance Test)? If it's close to your field's standard one of the many qualification
+Significance Test)? If it's close to your field's standard, one of the many qualification
 proposed by
 \href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
-  Hankins} to report your results? Can't you use expression such as {\em nearly
+  Hankins} might just do the trick. Can't you use expression such as {\em nearly
   acceptable level of significance (p=0.06)}, {\em very closely brushed the
@@
 If you're
-suffering from a bi-polar p-value disorder, however (a term coined by
+suffering from a bi-polar p-value disorder (a term coined by
 \href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
@@
 researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
-statement to explain p's correct usage \citep{wasserstein:2016,};
+statement to explain p's correct usage \citep{wasserstein:2016};
 Nature has issued a warning as well
@@
 really intend to plagiarize, you'll need to transform the text drastically to
-avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
+avoid detection by humans \citep{dorigo:2015} and more importantly, to avoid
 detection by dedicated software (e.g. iThenticate). This software is used by
@@
 
-Even if you avoid all the pitfalls discussed above, you're in the clear yet. Depending on the
+Even if you avoid all the pitfalls discussed above, you're not in the clear yet. Depending on the
 journal you target, you may still encounter problems with the review
@@
 you're likely to get caught sooner or later. The number of researcher to have never been caught is probably low; only the best can hope to be caught only after their death
-\citep{degroote:2016,}. But being caught while you're still breathing does not mean you career will come to
+\citep{degroote:2016}. But being caught while you're still breathing does not mean you career will come to
 an end. There is a set of simple rules to follow if you need to deny scientific misconduct:
